%%%% Acknowledgements page %%%%
\cleardoublepage % Clear the previous page
\phantomsection % Create Hyperref anchor
\addcontentsline{toc}{chapter}{Acknowledgements} % Add the abstract to the Table of Contents

\chapter*{Acknowledgements} % Abstract section, unnumbered ("*")
Firstly, I would like to thank Dr. Rajib Sinha for his advice and guidance throughout the entire development of this thesis, as well as his continued support to help me achieve my goals. To him and all the professors I ever had, I am grateful of their will to teach and share their knowledge and sapience with all of us students; it is a great task you carry on your shoulders and for that you have my heartfelt gratitude.

Thanks to all my fellow master students too. It has been a truly mentally engaging and welcoming two years. Especial mention is deserved by all the new friends I have made along this stay: Amanda, Clemens, Elin, Else, Jana, Micke, Sophia and many others for sure. It has been fantastic to share visions of the world together, questions, answers, meals, beers and laughs and hugs.

As much as to new, I am thankful to old friends scattered around the globe: Aitor, Albert, Arnau, Bernat, Borja, Carlos, Clàudia, Laura, Judith, Marc, Natàlia, Natxo, Néstor, Pau, Rafa. I look forward to meeting you once again and for many years, joking and laughing as ever before.

I could not stop to thank Dirk and Kathrin all their support and their wonderful reception at their home. It has been amazing to share your space for a year and a half. I wish we meet again in the future, to a cup of wine, to talk about the wonders of life.

To my parents and my brother, that have raised me and taught me. For the all the support and love.

To you, Raquel; words are not enough. Life by your side is so much brighter. Thank you.



\cleardoublepage % Clear the page for other sections (front matter or main matter)