\clearpage
\chapter{IPCC SSP1 storyline summary table}
\label{a:ssp1-summary-table}
%
\tref{t:appendix:ssp1-storyline-summary} corresponds to the summary of the original SSP1 scenario narrative. The original table contained the trends for the rest of the SSP scenarios. Reprinted from Global Environmental Change, \textbf{42}, Brian C. O’Neill, Elmar Kriegler, Kristie L. Ebi, Eric Kemp-Benedict, Keywan Riahi, Dale S. Rothman, Bas J. van Ruijven, Detlef P. van Vuuren, Joern Birkmann, Kasper Kok, Marc
Levy, William Solecki, \textit{The roads ahead: Narratives for shared socioeconomic pathways describing world futures in the 21st century}, 169-180, Copyright (2017), with permission from Elsevier. License number 4111240276671.

{\scriptsize
\begin{longtable}{p{5cm}p{9cm}}
\caption[IPCC's SPP1 storyline summary table.]{IPCC's SPP1 storyline summary table. Adapted from \textcite{oneill2017_roadsaheadNarratives}.}\\
\toprule
SSP element & SSP1 trend \\
\midrule
\endfirsthead
\caption*{(\emph{continued}) IPCC's SPP1 storyline summary table. Adapted from \textcite{oneill2017_roadsaheadNarratives}.}\\
\toprule
SSP element & SSP1 trend \\
\midrule
\endhead
\bottomrule
\endfoot
\bottomrule
\addlinespace
\multicolumn{2}{l}{
\textsuperscript{*}\emph{HIC} stands for \emph{H}igh \emph{I}ncome \emph{C}ountries, \emph{MIC} for \emph{M}edium \emph{I}ncome \emph{C}ountries and \emph{LIC} for \emph{L}ow \emph{I}ncome \emph{C}ountries.}
\endlastfoot
\label{t:appendix:ssp1-storyline-summary}\textbf{Demographics} &  \\
Population growth & Relatively low \\
Fertility rate & Low in currently high- and low-fertility countries; medium in rich OECD countries. \\
Mortality & Low \\
Migration & Medium \\
Urbanization level & High \\
Urbanization type & Well managed \\ \addlinespace
\textbf{Human development} &  \\
Education & High \\
Health investments & High \\
Access to health facilities, water, sanitation & High \\
Gender equality & High \\
Equity & High \\
Social cohesion & High \\
Societal participation & High \\ \addlinespace
\textbf{Economy \& lifestyle} &  \\
Growth (per capita) & High in LICs\textsuperscript{*} and MICs\textsuperscript{*}, medium in HICs\textsuperscript{*} \\
Inequality & Reduced across and within countries \\
International trade & Moderate \\
Globalization & Connected markets, regional production \\
Consumption and diet & Low growth in material consumption, low-meat diets, first in HICs \\
\textbf{Policies \& institutions} &  \\
International cooperation & Effective \\
Environmental policy & Improved management of local and global issues; tighter regulation of pollutants \\
Policy orientation & Toward sustainable development \\
Institutions & Effective at national and international levels \\ \addlinespace
\textbf{Technology} &  \\
Development & Rapid \\
Transfer & Rapid \\
Energy tech. change & Directed away from fossil fuels, toward efficiency and renewables \\
Carbon intensity & Low \\
Energy intensity & Low \\ \addlinespace
\textbf{Environment \& natural resources} &  \\
Fossil constraints & Preferences shift away from fossil fuels \\
Environment & Improving conditions over time \\
Land use & Strong regulations to avoid environmental tradeoffs \\
Agriculture & Improvements in agricultural productivity; rapid diffusion of best practices
\end{longtable}
}