In order to develop a future vision that tells us how mobility is conceived in the year 2100, two main options are available: (a) write and justify a new vision from the ground up or (b) building upon already developed visions found throughout the literature. Both to reduce the time spent on this task and to increase the legitimacy\footnote{Given that no participatory process is carried to describe or develop the future vision and the corresponding backcasting, expert opinions, in the form of widely accepted scientific scenarios, are used.} of the result, the second option is chosen. \cref{ss:results:ssp-scenarios-candidate} deals with the selection of the scenario that forms the basis of the future mobility vision, which is actually developed in \cref{ss:results:ssp1-mob-development}. Finally, a transition-studies characterisation of the future vision and the current situation of mobility is given in \cref{ss:results:ssp1-mob-transition-char}.

\subsection{The SSP scenarios and the selected candidate}
\label{ss:results:ssp-scenarios-candidate}
The \gls{IPCC} has recently developed several scenarios that are the basis of their integrated climate change assessments \parencite{oneill2017_roadsaheadNarratives,vuuren2017_Energylanduse,fricko2017_markerquantificationShared,fujimori2017_SSP3AIMimplementation,calvin2017_SSP4worlddeepening,kriegler2017_Fossilfueleddevelopment}. These scenarios are called Shared Socio-economic Pathways (SSP) and are defined on the basis of \textit{qualitative narratives} that contain all the necessary information on global trends to enable a further quantification step, using Integrated Assessment Models (IAM), such as the IMAGE model \parencite{vuuren2017_Energylanduse}. Given that SSPs are not designed solely for the purpose of climate change studies, but are rather a description of world futures, they can be used in other disciplines and, particularly, in any kind of sustainability studies \parencite{oneill2017_roadsaheadNarratives}. Furthermore, the fact that the scenarios are developed in the form of a \textit{narrative} actually makes them closer to the concept of a ``vision'' than that of a traditional scenario: SSPs define final states, rather than trends or forecasts.

Among the five IPCC SSP scenarios\footnote{The original narratives of all SSP1, SSP2, SSP3, SSP4 and SSP5 scenarios and the explanation of the assumptions taken to develop them can be found in \textcite{oneill2017_roadsaheadNarratives}.}, SSP1 ``\textit{Sustainability -- Taking the green road}'' is the one that implies a lower level of both adaptation and mitigation challenges with respect to climate change. Moreover, it is the one that is more aligned with the concept of Sustainable Development, due to its relatively high performance in all three pillars of sustainability: environmental conservation, social and economic sustainability (at least, economic \textit{growth} per capita). Therefore, it is the selected SSP to extend by covering the mobility sector, in order to perform the backcasting process that will be used in \cref{s:results:backcasting-ssp1-mob} to identify the necessary changes and development goals to reach a sustainable transport system in the future. The extension of the scenario, developed as a qualitative narrative is called \textit{SSP1-MOB}, from here on.

\subsection[The SSP1 mobility extension]{The SSP1 mobility extension: a narrative for the future}
\label{ss:results:ssp1-mob-development}
A particular \textit{vision} of a future sustainable mobility system is outlined in SSP1-MOB. Note that it is not comprehensive description of the myriad of elements composing the system, because it would not be feasible and too many sources of uncertainty would be introduced. Rather, it deals with travel patterns and which travel modes are most common, provided the necessary elements and configurations that make these patterns possible. The features and trends of the vision are summarised in \cref{t:ssp1-mob-narrative-vars}; some of them are taken from the original SSP1 IPCC scenario, while the rest are developed for this thesis. The following is the narrated version of SSP1-MOB, describing the global situation of the mobility system in the year 2100:

\blockquote{\sffamily \textbf{SSP1-MOB narrative}\\Driven by an increasing level of awareness of the environmental and socio-economic impacts of the transportation system, the world has adopted a series of changes throughout the decades to reduce those. Technology-wise, vehicles have become more efficient and liquid hydrocarbon fuels are less carbon intensive and renewable (based on biofuels). More importantly, though, there has been a major shift in travel modes and, most importantly, total travel demand per capita has been reduced. However, the global absolute total demand has increased, due to economic growth and increases in the living standard of countries in Africa, Asia and South America.

An increase in urban density (1st), a change in land use patterns (2nd) and a de-centralisation of economic development hotspots (3rd) are at the core of the substantial change in travellers' needs and, thus, behaviour. More concentrated urban centres allow for a shortening of trip lengths, up to a point where cycling and walking are feasible alternatives. The size of cities, however, is kept below certain thresholds that permit, in principle, for a more livable and sustainable way of life. This indeed means that a de-centralisation process has taken place, from huge, unwieldy metropolis to medium-sized cities, allowing for (and requiring) a more horizontal economic and governance structure. Moreover, there has been a generalised backlash against single-use urban development, this is, there has been a move towards mixing cultural, residential, work, institutional and commercial uses. This form of urban development acknowledges the limitations of single-use schemes, such as isolation and automobility dependence. These de-centralisation and mixing trends allow people to avoid the need for relocation to find a job or, for the same matter, commute long distances. Instead, short to medium distances or travel times are the norm when commuting, thus preventing the further need and use of automobiles.

High education levels, widespread access to fast internet and changes in consumption patterns also contribute to lower travel demand. This change in consumption patterns ranges from (a) lower material use (de-materialization) to (b) higher adoption of low-meat diets that prevent the need to ship feedstock and processed foods or (c) a reduction of very carbon-intensive activities, such as tourism. Teleworking is increasingly adopted by companies and in other office-based jobs, allowing people to work from shared co-working facilities that are near home or to avoid commuting altogether. Travelling is discouraged by governments through economic policy instruments such as carbon and/or congestion taxes, road usage fees and by shifting investments and subsidies from private mobility schemes to public ones.

When it comes to travel mode alternatives, most of the demand is supplied through public transport, be it in the form of passenger rail, buses or aviation. An increased and continuous heavy investment in public transport infrastructure (an extensive railway network, for example) has enabled fast, secure and low-carbon transport options for the majority of the population, which lives in more concentrated urban areas. High speed trains cover the demand for regional and national trips and even international trips (whenever the distance is not excessive). Regular electric trains and trams are the main mode of transport for interurban commuters and travellers. For less accessible areas, efficient, bio-fuelled, hybrid and electric buses are used. Fast and reliable hybrid or electric buses are also used for relatively short trips within cities. Aviation is used primarily for international travel, but the economic incentives for low-cost trips have been reduced; the market has been regulated and stringent regulations on emissions and other indirect impacts have been put in place. With regards to energy carriers for aviation, the main feasible alternative are highly energy-dense biofuels. In general, public transport poses to be a cheaper and more affordable option than automobile-based mobility, both for commuting and for leisure travel. Moreover, the perception of public mobility has changed and is now regarded as the best way to travel, due to higher levels of comfort, security and high reliability.

Even though public transport is the main and dominant travel mode, private mobility (automobility) is still a relevant mode in terms of total travel demand. The main reason for the long term survival of this mode is the higher degree of accessibility it provides, especially in remote, rural areas. While accessibility is kept at a high level thanks to this alternative, automobile (cars or two-wheelers) ownership rates are low. Car sharing is common and most urban communities benefit from reduced fleets thanks to carpooling, which is also commonly available and well accepted by the public. Within the specific travel market that automobility now occupies, battery electric vehicles are the main car-based technological option used for short to medium ranged trips, such as commuting. Hydrogen-fuelled vehicles take the lead for longer trip distances. The cultural perception of the automobile as a status symbol has declined, in favour of the more environmentally sustainable public transport and slow modes like cycling and walking. Furthermore, the discourse around individual freedom that once legitimised automobility has been deeply challenged by the increasingly sustainability-concerned population.

Finally, slow travel modes such as walking and cycling have been adopted by many to cover the shortest inner-urban trips, especially amongst the youngest. Cycling lanes are an integral part of every urban area road network and public cycling facilities, such as parking stations or even public bike rental service schemes, are commonplace. Traffic regulation has been changed to prioritise and ensure the safety of both cyclists and pedestrians. Ample footpaths (sidewalks) provide not only the space for walking but also a more ``livable'' urban environment.
}

{\scriptsize
\begin{longtable}{p{3cm}p{3.5cm}p{8cm}}
\toprule
Category & Variable & Trend \\ \midrule
\multicolumn{3}{l}{\textbf{SSP1 -- Source: O'Neill et al., 2017}}\\
\textit{Demographics} & Population growth & Relatively low\\
\textit{} & Fertility rate & Low in currently high- and low-fertility countries; medium in rich OECD countries.\\
\textit{} & Mortality & Low\\
\textit{} & Migration & Medium\\
\textit{} & Urbanization level & High\\
\textit{} & Urbanization type & Well managed\\
\textit{Human development} & Education & High\\
\textit{} & Health investments & High\\
\textit{} & Access to health facilities, water, sanitation & High\\
\textit{} & Gender equality & High\\
\textit{} & Equity & High\\
\textit{} & Social cohesion & High\\
\textit{} & Societal participation & High\\
\textit{Economy \& lifestyle} & Growth (per capita) & High in LICs and MICs, medium in HICs\\
\textit{} & Inequality & Reduced across and within countries\\
\textit{} & International trade & Moderate\\
\textit{} & Globalization & Connected markets, regional production\\
\textit{} & Consumption and diet & Low growth in material consumption, low-meat diets, first in HICs\\
\textit{Policies \& institutions} & International cooperation & Effective\\
\textit{} & Environmental policy & Improved management of local and global issues; tighter regulation of pollutants\\
\textit{} & Policy orientation & Toward sustainable development\\
\textit{} & Institutions & Effective at national and international levels\\
\textit{Technology} & Development & Rapid\\
\textit{} & Transfer & Rapid\\
\textit{} & Energy tech. change & Directed away from fossil fuels, toward efficiency and renewables\\
\textit{} & Carbon intensity & Low\\
\textit{} & Energy intensity & Low\\
\textit{Environment \& natural resources} & Fossil constraints & Preferences shift away from fossil fuels\\
\textit{} & Environment & Improving conditions over time\\
\textit{} & Land use & Strong regulations to avoid environmental tradeoffs\\
\textit{} & Agriculture & Improvements in agricultural productivity; rapid diffusion of best practices\\ && \\
\multicolumn{3}{l}{\textbf{SSP1 (implementation) -- Source: van Vuuren et al., 2017}}\\
\textit{Energy demand} & Transport & Lower share of income spent on transport leading to less kms travelled. More travel time (0.5 min/day increase each year) resulting in less shift to faster mode. Preference for public transport, car sharing, and faster increase in efficiency (10\% in 2100).\\
\textit{Energy supply and conversion} & Fossil fuels & Global trade of fuels; and median technology development for fossil fuel extraction technologies.\\
\textit{} & Bio-energy & Traditional bio-fuels mostly phased out around 2030; bio-fuels in transport taxed for possible biodiversity damage; less potential based on nature reserves but increased from abandoned lands; high yields; improved efficiencies and costs of biofuel production technologies; residues based on Daioglou et al. (2016).\\
\textit{Other (in-text)} & Sustainable development agenda & In order to pursue an ambitious agenda, the main requirement is the further growth of societal support for such a strategy combined with an actual change in investment patterns (Ocampo, 2011).\\
\textit{} & Socio-technical transition & The breaking off the current trends can be achieved through the up-scaling of niches to a mainstream (regime) level (Geels, 2012). Elements of the transition include the adoption of green growth concepts, the recent approval of the SDGs but also the rapid decline in costs of key technologies such as PV and electric batteries (IRENA, 2014; Nykvist and Nilsson, 2015).\\
\textit{} & Risks of the SSP1 world & a) non-performance of the technology; b) rebound impact of efficiency; c) possible tensions associated with free-rider behaviour and d) a potential push-back from actors whose interests are not ensured in this storyline.\\
\textit{} & Transport energy & Up to 2050, alternative fuels rapidly gain market shares, but oil remains important. In 2100, there is a dominant position of electric and hydrogen-fuelled drive-trains in road transport; biofuels become the most important for aviation and trucks.\\
\textit{} & Electricity use & Rapid growth\\
\textit{} & Electricity production & 65\% renewables by 2100.\\ \bottomrule
\caption{Qualitative variables and trends underlying to the \gls{SSP1-MOB} narrative.}
\label{t:ssp1-mob-narrative-vars}
\end{longtable}
}

\subsection{Characterising the transition to SSP1-MOB}
\label{ss:results:ssp1-mob-transition-char}

